Supplementary Information

### 2020-09-16 writing/transect_supplement.Rmd
address most reviewer comments in intro

(ref:buffer-pcoa) For each sequencing strategy, only those sampling locations with more than 100 reads each for all three year/preservation buffer combinations were included.

@@

(ref:buffer-compare-long) Comparison of read counts by taxonomic groups for different preservation buffers (Xpedition vs. LifeGuard) and sampling year, for long amplicon libraries.

@@

(ref:rDNA) Portion of the rDNA showing the 5.8S rDNA, partial SSU and LSU rDNA (thick lines), and internally transcribed spacer (ITS) regions (thin black lines).  D1-3 (grey) represent the first three variable regions in LSU, while LSU1-4 (black) represent the conserved regions. Primer sites used in this study are indicated in red (forward primers) and blue (reverse primers), and the resulting amplicons are shown with green braces.

@@

(ref:phylotax) In the example, a clade includes  seven OTUs (A-F), which have been identified by two methods as belonging to taxa "Tax1" or "Tax2", or are unidentified ("unk"), as shown in the tip labels.
No taxon is assigned at node\ 1, because one of the child branches (A) is completely unassigned.
No taxon is assigned at node\ 2, because the assignments at C and F are inconsistent.
Node\ 3 is assigned to Tax1 because this is consistent with at least one of the assignments for both B and C.
Node\ 4 (and thus also node\ 5) is assigned to Tax2 because this is consistent with at least one of the assignments for D and F, and because E is completely unassigned.

@@

(ref:sample-depth) DNA concentrations after extraction (leftmost column) and PCR (second and third columns), and sequencing depth (right three columns) along transects at the two sites Ang and Gan for the years 2015 and 2016.
Sequencing reads which were filtered out during quality control are colored dark grey.
Dotted horizontal line at 100\ reads indicates cutoff for inclusion in community analysis.
2016 samples were preserved using two different methods (LifeGuard, Xpedition), while 2015 samples were preserved only using Xpedition.

>>>>

(ref:buffer-pcoa) For each sequencing strategy, only those sampling locations with more than 100 reads each for all three year/preservation buffer combinations were included.
<!-- R3: your caption isn’t in line with your axes. Your axes say MDS1 and MDS2 – so it looks like a NMDS to me. But you caption says PCA. There is also insufficient information to jusdge this figure - No information on if reads were normalized or not, or what beta diversity metric this is based on, etc-->

@@

(ref:buffer-compare-long) Comparison of read counts by taxonomic groups for different preservation buffers (Xpedition vs. LifeGuard) and sampling year, for long amplicon libraries.
<!-- R3: I have no idea how to interpret these figures. More explanation is needed!-->

@@

(ref:rDNA) Portion of the rDNA showing the 5.8S rDNA, partial SSU and LSU rDNA (thick lines), and internally transcribed spacer (ITS) regions (thin black lines).  D1-3 (grey) represent the first three variable regions in LSU, while LSU1-4 (black) represent the conserved regions. Primer sites used in this study are indicated in red (forward primers) and blue (reverse primers), and the resulting amplicons are shown with green braces.
<!-- R3: Figure S4 is useful and should be in the main paper. -->

@@

(ref:phylotax) In the example, a clade includes  seven OTUs (A-F), which have been identified by two methods as belonging to taxa "Tax1" or "Tax2", or are unidentified ("unk"), as shown in the tip labels.
No taxon is assigned at node\ 1, because one of the child branches (A) is completely unassigned.
No taxon is assigned at node\ 2, because the assignments at C and F are inconsistent.
Node\ 3 is assigned to Tax1 because this is consistent with at least one of the assignments for both B and C.
Node\ 4 (and thus also node\ 5) is assigned to Tax2 because this is consistent with at least one of the assignments for D and F, and because E is completely unassigned.
<!-- Is there an error in the legend? It appears that node 3 is assigned to Taxa 1 based on box color coding and node 4 to Taxon 2 based on different box color coding. In the legend, it states that node 3 is assigned to Taxa 1, but there are three matches to Taxon 2 at that node and Taxon 2 is presented in Salmon color consistent with the box color for node 3. As such, I think the authors meant to designate node 3 as being assigned to Taxon 2. If this is wrong, then more details in the legend explaining why the greater presence of matches to Tax2 yet assignment to Tax1 is needed. -->

@@

(ref:sample-depth) DNA concentrations after extraction (leftmost column) and PCR (second and third columns), and sequencing depth (right three columns) along transects at the two sites Ang and Gan for the years 2015 and 2016.
Sequencing reads which were filtered out during quality control are colored dark grey.
Dotted horizontal line at 100\ reads indicates cutoff for inclusion in community analysis.
2016 samples were preserved using two different methods (LifeGuard, Xpedition), while 2015 samples were preserved only using Xpedition.
<!-- R3: please enlarge. This is too small. -->
